
\documentclass{scrartcl}

\input{winstonPreambleDefaults.tex}

\usepackage{listings}
\lstset{
basicstyle=\small\ttfamily,
language={[LaTeX]TeX},
}

\usepackage{showexpl}
\usepackage{bookmark}

\title{Documenting these files}
\author{Winston Cheong}
\date{2024 Oct 13}

\begin{document}
\maketitle

I want the majority of these files to be frozen.
Very little tweaking should be needed.

The exception should be \texttt{winstonMathMacros.tex} and
\texttt{winstonOtherMacros.tex}.
It is reasonable for these two to change, as I come up with reasonable macros that can be used in all of my note files.

Theorem setup may be finicky. For some files, may need to copy contents into the
specific file, and adjust from there.



Using this reintroduces dependencies. I have to be careful not to break things.

\section{Structure}

The main preamble is \texttt{winstonPreambleDefaults.tex}.

We want to have a decoupling between syntax and semantics.
For categories, a naming convention of \verb|\cat<>| is perhaps reasonable.

For letter categories, it would dispatch to \verb|\mathcal| or \verb|\mathsf| depending on preference.

Maybe for easy rewriteability, we introduce a \verb|\catLetterStyle| command,
which is a macro for whichever thing to use (can be redefined in specific
documents)

Things might be more tricky with named categories. There can be some stylistic
choices taken by different authors.

The category of $A$-$B$ bimodules ($A$, $B$ can be rings or DG algebras) can be written as:
\begin{itemize}
    \item $A\text{-}B\text{-}\mathsf{Mod}$
    \item $A\text{-}\mathsf{Mod}\text{-}B$
    \item ${}_A\mathsf{Mod}_{B}$
\end{itemize}

\rulehere

Wedhorn's notation for categories is to surround with parens.
Boldface or sans-serif are used by other authors.

\section{Test Lie groups}

$\GL(n)$, $\SL(n)$, $\SO(n)$, $\Sp(n)$, $\SU(n)$, $\U(n)$

\section{Test Lie algebras}

The commands \verb|\u|, \verb|\so|, \verb|\sp| already exist in \TeX.

I'm considering using the prefix \texttt{lie} before the name of the algebra / symbol to make the macro name.

So
\begin{LTXexample}[pos=b]
$\liegl(n)$, $\liesl(n)$, $\lieso(n)$, $\liesp(n)$, $\liesu(n)$, $\lieu(n)$
\end{LTXexample}


I suppose that generally, \texttt{lie} can be used as a prefix for \verb|\mathfrak|.
The prefix \texttt{k} can also be used.

\section{Test paired delimiters}
\verb|\gens{}| and \verb|\ideal{}|

$\gens{a,b}$,
$\ideal{x,y}$,
\[
\gens{\frac12, 5}, \quad
\gens*{\frac12, 5}
\]



\end{document}